Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-18 Article.tex
Correction of Section 2

% This is used to add comments into the text
\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}\\#1}}\endgroup} }

@@

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050^\circ\text{C} -1250^\circ$C). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
\end{abstract}

@@

%----------------------------------------------
\section{ Materials and Experiments \label{sec:Materials}}
%----------------------------------------------
%----------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------
The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}. Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm. Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$. Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests. The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients. Then cooled to test temperature where the specimen is held $1$ minute before deformation. After compression the specimen is quencted rapidly for microstructure studies. The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/Gleeble-3800}
\caption{Gleeble 3800 simulator system}
\label{fig:Gleeble3800}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/GleebleDesign}
\caption{Schematic diagram of the experimental process.}
\label{fig:Heating}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
\begin{tabular}{lcccccccc}
\hline
C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
\hline
 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
\hline
\label{tab:Composition}
\end{tabular}
\end{table}
%------------------------------------------------------------------------
\subsection{Flow stress behavior}
%------------------------------------------------------------------------
The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}. From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature. It should be noted that the strain influences the flow stress. Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test. The peak stress value increases with strain rate but decreases with temperature. For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test. The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test. For low strain rates, lubrication is lost over time and therefore friction occurs. This results in a progressive increase in stress.

To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX). At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening. As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC. During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains. The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress. DRX consists of the germination of new grains, at the borders or inside the initial grains. These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy. As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression. As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate. Indeed, most of the grain boundaries start to form new grains. The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/BeforeCompM}
\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
\label{fig:BeforeCompM}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/AfterCompM}
\caption{Optical micrograph of AISI P20 alloy after hot compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
\label{fig:AfterCompM}
\end{figure}

@@

\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot{\varepsilon}^*\right)\left(1-T^{*^m}\right)

@@

Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma^y_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent. $C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively. $\mdot{\varepsilon}^*$ is the dimensionless strain rate which is given by $\mdot{\varepsilon}^* = \mdot{\varepsilon^p}/\mdot{\varepsilon_0}$. $\mdot{\varepsilon^p}$ and $\mdot{\varepsilon_0}$ are strain rate and reference strain rate respectively. $T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature (1460$^\circ$C in our case) and reference temperature respectively. For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050^\circ$C respectively and the value of $A$ is $43.0988$ MPa. Here after datailed the steps for determination of the JC model parameters.

@@

\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050^\circ$C and $0.1$}

@@

\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot{\varepsilon}^*

@@

As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately. Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}. But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot{\varepsilon}^{p^{m_3}}e^{\frac{m_4}{\varepsilon^p}}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot{\varepsilon}^{p^{m_7T}}T^{m_8}

@@

Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot{\varepsilon}^p$ strain rate and $T$ temperature. The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case. Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS}. It appears that this model as well as the previous ones do not predict the experimental well and the gap is relatively large. This shows that this model is not appropriate for the characterisation of this alloy.

@@

The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material. Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot{\varepsilon}^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation. This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature. The following equations describe the Arrhenius model.

@@

\mdot{\varepsilon}^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)

@@

\mdot{\varepsilon}^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)

@@

\mdot{\varepsilon}^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)

@@

Where $\mdot{\varepsilon}^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:

@@

Z = \mdot{\varepsilon}^p\exp\left(\frac{Q}{RT}\right)

@@

\ln \sigma^y = \frac{1}{n_1}\ln \mdot{\varepsilon}^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}

@@

\sigma^y = \frac{1}{\beta}\ln \mdot{\varepsilon}^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}

@@

\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot{\varepsilon}^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}

>>>>

% This is used to add comments into the text
\usepackage{soul} %Can also be used to highlight text with \hl{highlighted text}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150} % VaporWave color palette
\DeclareRobustCommand{\OP}[1]{ {\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{Olivier Pantal\'e:}#1}}\endgroup} }

@@

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050\text{°C}-1250\text{°C}$). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050$°C and $1100$°C  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
\end{abstract}

@@

%----------------------------------------------
\section{Materials and Experiments\label{sec:Materials}}
%----------------------------------------------

%----------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}. Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm. A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050$°C, $1100$°C, $1150$°C, $1200$°C and $1250$°C with the six strain rates of $0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$, $1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$ and $5.0~\text{s}^{-1}$.

\begin{table}[h!]
\centering
\caption{Chemical composition of AISI P20 steel, Fe = balance.}
\begin{tabular}{lccccccc}
\hline
Element & C & Mn & Mo & Si & Ni & Cr & Cu\\ \hline
Wt~\% & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17\\ \hline
\label{tab:Composition}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}

Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing. As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260$°C with a heating rate of $2$°C/s and held at this temperature for $5$~min to eliminate thermal gradients. They were then cooled with a rate of $1$°C/s to the test temperature and then held at constant temperature for $1$~min before deformation. During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine. After compression, the specimen is quickly quenched to freeze its microstructure for later analysis. Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $R_0$ are the height and radius before compression and $h$, $R_M$ and $R_T$ are the height, large radius and small radius of the specimen after compression, respectively.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process.}
\label{fig:GleebleProcess}
\end{figure}

%------------------------------------------------------------------------
\subsection{Compression tests results}
%------------------------------------------------------------------------

The set of flow stress $\sigma^y$ versus plastic strain $\varepsilon^p$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}. The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon^p$ but decreases with increasing temperature $T$. It should be noted that the plastic strain also influences the flow stress. Indeed, for the lowest strain rates $\mdot\varepsilon^p$, the flow stress $\sigma^y$ increases with the plastic strain $\varepsilon^p$ until a value of about $\varepsilon^p=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test. For the highest strain rates ($1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$, and $5.0~\text{s}^{-1}$), the flow stress increases throughout the test. One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test. For low strain rates, the effect of lubrication decreases over time and thus friction increases. This results in a progressive increase of the flow stress.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX). At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon). As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRC. This DRC mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary. Some of these dislocations reorganize and then form sub-grains within the initial grains of the material. The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress. The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains. These two phenomena explain the different shapes of the flow stress curves observed for this alloy. As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260$°C before and after the compression phase. As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \OP{What are the temperature and strain rate related with this micrography}. From the results reported in Figure \ref{fig:rawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{Figures/BeforeCompM}
\caption{Before hot compression}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{Figures/AfterCompM}
\caption{After hot compression}
\end{subfigure}
\caption{Optical micrographs of the AISI P20 steel before and after hot compression.}
\label{fig:Micrography}
\end{figure}

@@

\sigma^y = \left(A + B\varepsilon^{p^n}\right)\left(1+C\ln\mdot\varepsilon^*\right)\left(1-T^{*^m}\right)

@@

Where $\sigma^y$ is the equivalent stress flow stress, $\varepsilon^p$ is the plastic strain, ($A=\sigma^y_0$) is the elastic limit of the material, $B$ is the strain hardening's coefficient, $n$ is the strain hardening's exponent. $C$ and $m$ are the material constants that describe the strain rate hardening and thermal softening exponent respectively. $\mdot\varepsilon^*$ is the dimensionless strain rate which is given by $\mdot\varepsilon^* = \mdot\varepsilon^p/\mdot\varepsilon_0$. $\mdot\varepsilon^p$ and $\mdot\varepsilon_0$ are strain rate and reference strain rate respectively. $T^{*^m} = (T-T_0)/(T_m - T_0)$ is homologous temperature where $T, T_m$ and $T_0$ are the déformation temperature, meltinng temperature ($1460$°C in our case) and reference temperature respectively. For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $2.0$ and $1050$°C respectively and the value of $A$ is $43.0988$ MPa. Here after datailed the steps for determination of the JC model parameters.

@@

\caption{Relationship between $ln(\sigma^y -A)$ and $\ln(\varepsilon^p)$ at $1050$°C and $0.1$}

@@

\frac{\sigma^y}{A + B\varepsilon^{p^n}} = 1 + C\ln\mdot\varepsilon^*

@@

As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately. Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}. But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot\varepsilon^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

\sigma^y = Ae^{m_1T}\varepsilon^{p^{m_2}}\mdot\varepsilon^{p^{m_3}}e^{\frac{m_4}\varepsilon^p}(1+\varepsilon^p)^{m_5T}e^{m_6\varepsilon^p}\mdot\varepsilon^{p^{m_7T}}T^{m_8}

@@

Where $\sigma^y$ is the flow stess, $\varepsilon^p$ strain, $\mdot\varepsilon^p$ strain rate and $T$ temperature. The other coefficients $A$ and $m_j$ are model constants up to $m_5$ for our case. Comparison of predicted values of the HS model and experimental values is shown in Figure \ref{fig:iCorrelationHS}. It appears that this model as well as the previous ones do not predict the experimental well and the gap is relatively large. This shows that this model is not appropriate for the characterisation of this alloy.

@@

The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material. Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation. This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature. The following equations describe the Arrhenius model.

@@

\mdot\varepsilon^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)

@@

\mdot\varepsilon^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)

@@

\mdot\varepsilon^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)

@@

Where $\mdot\varepsilon^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:

@@

Z = \mdot\varepsilon^p\exp\left(\frac{Q}{RT}\right)

@@

\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}

@@

\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}

@@

\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
